---
title: "Halloween Candy Data Analysis, 2015-2017"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
candies <- read_csv(here::here("clean_data/clean_candies.csv"))
```

## Task 4 - Halloween Candy Data

The raw data analysed by this project is in files boing-boing-candy-2015.xlxs, boing-boing-candy-2016.xlxs and boing-boing-candy-2017.xlxs. These files are located in the `raw_data` folder.

More information on this data is available [here](https://www.scq.ubc.ca/so-much-candy-data-seriously/).


## Notes on data cleaning

 * The three datasets have been combined together with `rbind()`.
 
 * The column `country` is particularly messy and will require some 'hard coding'.
```{r}
# After the cleaning, this is what it looks like
candies %>% 
        group_by(country) %>% 
        summarise(count = n()) %>% 
        arrange(desc(count))
```
 * For the last three questions, count despair as -1, joy as +1, and meh as 0.
 
 * As an observation, the 2015 data lacks the meh option.
 
 * A timestamp is roughly used as ID in 2015 and 2016, in 2017 there's an actual ID. All three values can go in the same column. I converted the timestamps into character type and proceeded to merge.
 
 * Some age values have been recovered from the country column.
 
 * Some country values have been recovered from the region column.
 
 * Some columns are irrelevant for the analysis questions. I have removed those.
 
 * Some columns e.g. 'mary janes' and 'anonymous brown globs' seem to be referring to the same candy, but I will leave them as separate candies since people have rated them differently for the same year.
 
 * IN PROGRESS Filter out rows with no info i.e. no ratings given.
 
 * I assume that covert political questions in the form of M&M colour are also irrelevant.
 
 * Column names have to match so they can be combined. For this purpose I have written a helper function that prints unmatched names.
 
 * Pivot all the candy names and ratings into a `candy_name` and `rating` column.
 
 * `going_out` column converted to boolean type.
 
 * Admitted only ages within a 2 to 99 range.
 
 * I have purposefully left in some things that are not candies e.g. *broken glow sticks*, provided they're things one could get whilst trick or treating.
 

## Analysis questions

### What is the total number of candy ratings given across the three years?
Number of candy ratings to be counted, not the number of raters. Missing values to be excluded.
```{r}
candies %>%
        filter(!is.na(rating)) %>% 
        nrow()
```


### What was the average age of people who are going out trick or treating?
```{r}
candies %>% 
        filter(going_out == T) %>% 
        summarise(average_age = mean(age, na.rm = T))
```
### What was the average age of people who are **not** going out trick or treating?
```{r}
candies %>% 
        filter(going_out == F) %>% 
        summarise(average_age = mean(age, na.rm = T))
```

### For each of joy, despair and meh, which candy bar received the most of these ratings?
```{r}
candies %>% 
        group_by(rating, candy_name) %>% 
        summarise(count = n()) %>% 
        slice_max(count)
```
### How many people rated Starburst as despair?
```{r}
candies %>% 
        filter(candy_name == "starburst" & rating == -1) %>% 
        nrow()
```
Note, since no one rated a candy more than once these are all distinct people.

### What was the most popular candy bar by this rating system for each gender in the dataset?
```{r}
candies %>%
        group_by(gender, candy_name) %>% 
        summarise(popularity = sum(rating, na.rm = T)) %>% 
        slice_max(popularity, n = 3)
```
I have picked out the **three** most popular ones to see if there was some variation with gender.

### What was the most popular candy bar in each year?
```{r}
# First let's sort the table by year
candies_by_year <- candies %>%
        select(id, candy_name, rating) %>%
        mutate(id = case_when(
                str_detect(id, "2015") ~ 2015,
                str_detect(id, "2016") ~ 2016,
                TRUE ~ 2017))

candies_by_year %>%
        group_by(id, candy_name) %>% 
        summarise(popularity = sum(rating, na.rm = T)) %>%
        slice_max(popularity, n = 3)
```

### What was the most popular candy bar for people in US, Canada, UK, and all other countries?
```{r}
candies %>%
        group_by(country, candy_name) %>% 
        summarise(popularity = sum(rating, na.rm = T)) %>% 
        slice_max(popularity, n = 3)
```