---
title: "Cake Ingredients"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
```{r include=FALSE}
library(tidyverse)
library(here)
cakes <- read_csv(here("clean_data/clean_cakes.csv"))
```

The main data is in the file cake-ingredients-1961.csv, there is supplementary data that converts from short form ingredients to long form in cake_ingredient_code.csv.
<br>

### Some cleaning notes

* The raw data is not in tidy format, I have wrangled it so the clean data is.

* The final dataframe has actual ingredient names, not the abbreviations. These were previously found in cake_ingredient_code.csv

* Renamed some columns so the types of values they contain are clearer.

* I have formatted amounts and measurement units.

* There is one row per ingredient and cake. So I have removed the rows where the amount of ingredient is `NA`.

<br>

### Analysis questions
<br>

#### Which cake has the most cocoa in it?
```{r}
cakes %>% 
  filter(ingredient == "Cocoa") %>%
  slice_max(amount, n = 2)
```
The One Bowl Chocolate seems to be the winner, other cakes only have one tablespoon.
<br><br>

#### For sponge cake, how many cups of ingredients are used in total?
```{r}
cakes %>% 
  filter(cake_name == "Sponge" & measure_unit == "cup") %>% 
  summarise(total_cups = sum(amount))
```
<br><br>

#### How many ingredients are measured in teaspoons?
```{r}
cakes %>%
  distinct(ingredient, measure_unit) %>% 
  filter(measure_unit == "teaspoon")
```
It seems that 8 ingredients are measured in teaspoons.
<br><br>

#### Which cake has the most unique ingredients?
```{r}
cakes %>% 
  group_by(cake_name) %>% 
  summarise(unique_ingredients = n()) %>% 
  slice_max(unique_ingredients, n = 5)
  
```
We have a tie for the first spot with 11 unique ingredients.
<br><br>

#### Which ingredients are used only once?
```{r}
cakes %>% 
  group_by(ingredient) %>% 
  summarise(times_used = n()) %>% 
  slice_min(times_used)
```